Modern Physics Laser Scanning Project

### 2016-06-17 paper/paper.tex
update to paper

\documentclass[letterpaper, 12pt]{article}
\usepackage{circuitikz}
\usepackage{listings}
\usepackage[pdf]{pstricks}
\usepackage{pst-optexp}

@@

\begin{circuitikz}
  \draw
  (0,0) to [battery](3,0)
  to [european resistor](6,0)
  to [american resistor](7,3)
  to [short](4,1)
  to [short](4,0);
\end{circuitikz}

\begin{lstlisting}[language=C,showstringspaces=false]
  /**
   * Base code for Arduino when scanning 1 dimensionally.
   */

>>>>

\documentclass[letterpaper, 12pt]{article}
\usepackage{graphicx}
\graphicspath{ {pictures/} }
\usepackage{listings}
\usepackage[pdf]{pstricks}
\usepackage{pst-optexp}

@@

\begin{figure}
  \centering
  \includegraphics[width=12cm,height=9cm]{circuit}
  \caption{Diagram of Components}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=9cm,height=12cm]{setup}
  \caption[caption]{3D printed components, CADs available here:\hspace{\textwidth}https://www.github.com/omgimanerd/im-firing-my-lazer}
\end{figure}

\section{Experimental Procedure}

\begin{lstlisting}[language=C,showstringspaces=false]
